Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-03-09 eswc-2012/phdsymp.tex
against SQL
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@171 43ef1190-90fd-4dd7-a769-d0121f02b80e
Comment out sections that should be changed
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@172 43ef1190-90fd-4dd7-a769-d0121f02b80e

  Discontent with current state of the art in benchmarking prompts the
  author to focus on the evaluation problem and to investigate whether
  we can provide better advices to new users selecting a SPARQL engine
  to use.
\end{abstract}

@@

@@

With the currently published benchmarks, it is up to the user to
select an engine with the best characteristics, relative to their own
expected application. New users often are unable to formulate
\emph{any} relevant expectations. For these users, the wide variety of
benchmarks, for instance by the TPC, offers little help as a thorough
understanding of the benchmarks and what they measure is required to
select an engine. To help these users, we should ask ourselves:
Can we collapse all the metrics into a single \emph{test
  statistic} that can summarize the performance of the engine as a
whole? Also, can we provide a system for developers that they can use
to see if any changes they do to the engine can have unexpected adverse
effects on other parts of the system? For those who can formulate
relevant expectations, weighing different parts of the system or
metrics is more useful and will yield a more tenable answer, and
motivates the question: Can we use the system to better find the
distinguishing characteristics so that we can return a question that
will actually help new users of SPARQL engines to chose one that meets
their needs?

The above relies on data and queries that are representative of the
system as a whole. It is often asserted that it is not possible to
create a ``one-size-fits-all'' benchmark but answering the above
question requires such a benchmark. The relative simplicity of RDF and
SPARQL may make this feasible.

@@

With this analysis, I speculate based on superficial experience with
factorial designs and analysis of variance that certain estimated
coefficients can be exposed in the service description to give
federated query engines assistance in optimizing for performance
characteristics of certain SPARQL implementations. Adjusting how
different features are weighed will help those who know details of
their expected SPARQL use and normalization-techniques of the weights
will answer the special case of ``the best general-purpose SPARQL
engine''.

>>>>

%   Discontent with current state of the art in benchmarking prompts the
%   author to focus on the evaluation problem and to investigate whether
%   we can provide better advices to new users selecting a SPARQL engine
%   to use.
\end{abstract}

@@

The prior art in database theory is extensive, but I intend to focus
on aspects that sets SPARQL apart from e.g. SQL, like the quad model,
that it is a Web technology, or that data are commonly very
heterogenous.

@@

% With the currently published benchmarks, it is up to the user to
% select an engine with the best characteristics, relative to their own
% expected application. New users often are unable to formulate
% \emph{any} relevant expectations. For these users, the wide variety of
% benchmarks, for instance by the TPC, offers little help as a thorough
% understanding of the benchmarks and what they measure is required to
% select an engine. To help these users, we should ask ourselves:
% Can we collapse all the metrics into a single \emph{test
%   statistic} that can summarize the performance of the engine as a
% whole? Also, can we provide a system for developers that they can use
% to see if any changes they do to the engine can have unexpected adverse
% effects on other parts of the system? For those who can formulate
% relevant expectations, weighing different parts of the system or
% metrics is more useful and will yield a more tenable answer, and
% motivates the question: Can we use the system to better find the
% distinguishing characteristics so that we can return a question that
% will actually help new users of SPARQL engines to chose one that meets
% their needs?

% The above relies on data and queries that are representative of the
% system as a whole. It is often asserted that it is not possible to
% create a ``one-size-fits-all'' benchmark but answering the above
% question requires such a benchmark. The relative simplicity of RDF and
% SPARQL may make this feasible.

@@

With this analysis, I speculate based on superficial experience with
factorial designs and analysis of variance that certain estimated
coefficients can be exposed in the service description to give
federated query engines assistance in optimizing for performance
characteristics of certain SPARQL implementations. 
%Adjusting how
%different features are weighed will help those who know details of
%their expected SPARQL use and normalization-techniques of the weights
%will answer the special case of ``the best general-purpose SPARQL
%engine''.
